Missing data: Current practice in football research and recommendations for reporting missingness

### 2020-09-03 paper/paper.Rmd
change description of the search, change PRISMA figure details, remove the table for the breakdown of the PRISMA

To estimate the proportion of articles that report missing data in
football research, we conducted a systematic search [@Schafer2002]. Football related
articles published in 2019 were studied. Three major sports medicine
databases (SPORTDiscus, Embase and Cinahl) were searched, using key
terms and search limits (Supplement 1). Included articles were: (a)
published in 2019; (b) written in English; (c) had an accessible
full-text; and (d) included quantitative data. The search process is
summarised in Figure 1.

@@

prisma(found = x,

found_other = x,

no_dupes = x,

screened = x,

screen_exclusions = x,

full_text = x,

full_text_exclusions = x,

qualitative = x,

quantitative = x,

@@

+---------------------------------+-----------------------------------+
| Imported                        | 3,863                             |
+=================================+===================================+
| After duplicates removed        | 1,954                             |
+---------------------------------+-----------------------------------+
| After title and abstract screen | 1,373                             |
+---------------------------------+-----------------------------------+
| Random sample full-text         | 199 (needed for 10% sample)       |
+---------------------------------+-----------------------------------+
| Full-text included              | 137                               |
+---------------------------------+-----------------------------------+
| Full-text excluded              | Full-text papers excluded (n=62)  |
|                                 | with reasons:                     |
|                                 |                                   |
|                                 | Qualitative study (n=)            |
|                                 |                                   |
|                                 | Not in english (n=)               |
|                                 |                                   |
|                                 | Unable to access full-text (n=)   |
+---------------------------------+-----------------------------------+

>>>>

To estimate the proportion of articles that report missing data in
football research, we conducted a systematic search [@Schafer2002] **(should this reference be here?)**. Football related
articles published in 2019 were studied. Three major sports medicine
databases (SPORTDiscus, Embase and Cinahl) were searched, using key
terms and search limits (Supplement 2). Included articles were: (a) written in English; (b) had an accessible
full-text; and (c) included quantitative data. The search process is
summarised in Figure 1.

@@

prisma(found = 3863,

found_other = NA,

no_dupes = 1909,

screened = 1954,

random_sample = 199,

full_text = 199,

full_text_exclusions = 62,

@@
